---
usethis::use_github()---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MeaslesMapR)
```

### plotCases

```{r}
#| label: plotCases

# plotCases
plotCases(region, legend = F)
```

When provided with region(s) and an optional legend specification, plotCases generates a line plot displaying the total cases for countries in the regions.

### mapRegion

```{r}
#| label: mapRegion

# mapRegion
mapRegion(region = "ALL", 
          year)
```

When provided with one or more regions and a year, mapRegion generates a leaflet map highlighting the specified region, with each country annotated by its corresponding measles cases per million, MCV1 vaccination coverage and nominal GDP for the selected year. By default, the region parameter includes all regions.

### summarizeYear

```{r}
#| label: summarizeYear

# summarizeYear
summarizeYear(year)
```

When provided with a year, summarizeYear generates a table where each row represents a region along with its average measles cases per million and average population. The table is sorted in descending order by average measles cases per million and uses a darker color gradient to visually indicate higher case counts.
