---
usethis::use_github()---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MeaslesMapR)
```

### plotCases

```{r}
#| label: plotCases

# plotCases
plotCases(region, legend = F)
```

When provided with region(s) and an optional legend specification, plotCases generates a line plot displaying the total cases for countries in the regions.

### summarizeYear

```{r}
#| label: summarizeYear

# summarizeYear
summarizeYear(year)
```

When provided with a year, summarizeYear generates a table where each row represents a region along with its average measles cases per million and average population. The table is sorted in descending order by average measles cases per million and uses a darker color gradient to visually indicate higher case counts.

### filter_data

```{r}
#| label: filter_data

# filter_data
filter_data(data)
```

A helper function that cleans the data loaded in from load_data().

### validateRegion

```{r}
#| label: validateRegion

# validateRegion
validateRegion(region, data)
```

A helper function that when given a region name and a data frame, checks whether the data frame contains data for that region.

### validateYear

```{r}
#| label: validateYear

# validateYear
validateYear(year1, year2 = NULL)
```

A helper function that given two years, checks that the years are actual years.

### load_data

```{r}
#| label: load_data

# load_data
load_data()
```

A function to load in the Measles data from tidytuesdayR.
